Preventing a Nuclear ISIL: \\Recommendations for United States Policy

### 2015-05-11 draft.tex
Added quote page before Chapter 1.
Finished cleaning up appendices, sub-final comments.

@@

\chapter{???????  Add all ACRONYMS to table, reduce line spacing ?????}

@@

\subsection{?????????  Generally speaking, this Appendix could use some references ???????????}

@@

\subsubsection{?????? Be good to color code according to TS, S, C, or unclassified ???????}

@@

Information sharing in the international IC is immensely more complicated than between internal U.S. agencies. The mere fact of declared opposition to ISIL is an insufficient basis for intelligence sharing alone.  Indeed, the U.S. various strained relationships with many allies in the fight against ISIL. It is assumed that information sharing on the ISIL issue would fall along lines consistent with historical cooperation levels. Cooperation levels can be divided into a simple system of three levels as shown in \autoref{tab:relation_table}.

\begin{table}
\centering
\begin{tabular}{|c|l|}
\hline
Levels & \multicolumn{1}{c|}{Definition}                                                                                                             \\ \hline
1      & Historically and currently close relationship (Great Britain, France, Canada)                                                    \\ \hline
2      & \begin{tabular}[c]{@{}l@{}}Neither good nor bad relations or recent downturn in relations \\ For example: Germany as neutral \cite{BBC2013} and Israel as recent downturn \cite{Goldberg2014}.\end{tabular} \\ \hline
3      & Historically and currently bad relationship (Russia, Jordan, Turkey, Egypt \cite{Office2010})                                                  \\ \hline
\end{tabular}
\caption{My caption}
\label{tab:relation_table}
\end{table}

\subsubsection{????????  This table needs a caption  ???????}

@@

\subsection{????????  This appendix needs references  ???????}

>>>>

\thispagestyle{empty}

\topskip0pt
\vspace*{\fill}

\begin{center}
 \enquote{\emph{One of the most important lessons of the Cold War was that incessantly worrying about the low-probability/high-impact cases was a mistake.}}

 - Kenneth Pollack

\end{center}

\vspace*{\fill}

@@

@@

% \subsection{?????????  Generally speaking, this Appendix could use some references ???????????}

@@

% \subsubsection{?????? Be good to color code according to TS, S, C, or unclassified ???????}

@@

Information sharing in the international IC is immensely more complicated than between internal U.S. agencies. The mere fact of declared opposition to ISIL is an insufficient basis for intelligence sharing alone.  Indeed, the U.S. has  various strained relationships with many allies in the fight against ISIL. It is assumed that information sharing on the ISIL issue would fall along lines consistent with historical cooperation levels. Cooperation levels can be divided into a simple system of three levels as shown in \autoref{tab:relation_table}.

\begin{table}[h]
\centering
\begin{tabular}{|c|l|}
\hline
Levels & \multicolumn{1}{c|}{Definition}                                                                                                             \\ \hline
1      & Historically and currently close relationship (Great Britain, France, Canada)                                                    \\ \hline
2      & \begin{tabular}[c]{@{}l@{}}Neither good nor bad relations or recent downturn in relations \\ For example: Germany as neutral \cite{BBC2013} and Israel as recent downturn \cite{Goldberg2014}.\end{tabular} \\ \hline
3      & Historically and currently bad relationship (Russia, Jordan, Turkey, Egypt \cite{Office2010})                                                  \\ \hline
\end{tabular}
\caption{Intelligence sharing cooperation levels for the U.S. }
\label{tab:relation_table}
\end{table}

@@

% \subsection{????????  This appendix needs references  ???????}
